---
title: "Lists"
---

```{r setup}
library(tidyverse)
library(repurrrsive)
library(broom)
names(sw_people) <- sw_people %>% map_chr("name")

# Toy data
set.seed(1000)
exams <- list(
  student1 = round(runif(10, 50, 100)),
  student2 = round(runif(10, 50, 100)),
  student3 = round(runif(10, 50, 100)),
  student4 = round(runif(10, 50, 100)),
  student5 = round(runif(10, 50, 100))
)

extra_credit <- list(0, 0, 10, 10, 15)

names(who) <- str_replace(names(who), "newrel", "new_rel")
tb <-  
  who %>%
  gather("codes", "n", 5:60) %>%
  separate(codes, c("new", "type", "sexage"), sep = "_") %>%
  select(-new, -iso2, -iso3) %>%
  separate(sexage, c("sex", "age"), sep = 1) %>%
  drop_na(n)
```

# Lists

## Your Turn 1

Run the code below, which displays a list. What do you see?

```{r}
sw_people
```

## Quiz

```{r}
vec <- c(-2, -1, 0)
lst <- list(-2, -1, 0)

abs(vec)
abs(lst)
```

## Your Turn 2

Who was taller Anakin Skywalker or Darth Vader? 
Use the RStudio Viewer to find the answer (in cm).

*Hint: View() sw_people*

```{r}

```

## Your Turn 3

Here are two subsetting commands. Do they return the same values? Run the code chunks below to confirm.

```{r}
a_list <- list(num = c(8, 9), 
               log = TRUE,    
               cha = c("a", "b", "c"))
```

```{r}
a_list["num"]
```

```{r}
a_list[["num"]]
```

# Mapping

## purrr


## Your Turn 4

Run the code in the chunk. What does it do?

```{r}
exams %>% map(mean)
```

## map shorthand


## Your Turn 5

Complete the code to apply the test below to every element of the list. Return the results as a vector.

`length(<input> == 10)`

```{r}
exams %>% ______(_________________)
```

## Your Turn 6

Recompute the grades by dropping the lowest score and then taking the mean of the rest, i.e. Return the results as a _double_ vector.

`(sum(<input>) - min(<input>)) / 9`

```{r}

```


## Your Turn 7

Compute a final grade for each student, where the final grade is the average test score plus any `extra_credit` assigned to the student. Return the results as a double (i.e. numeric) vector.

`mean(<exams>) + <extra_credit>`

```{r}
exams %>% 
  _________(____________, ~________________)
```

# List Columns

# Putting it all together

Predict TB cases in 2020 for Afghanistan

```{r}
tb %>% 
  filter(country == "Afghanistan") %>%
  group_by(year) %>% 
  summarise(n = sum(n)) %>% 
  lm(n ~ year, data = .) %>% 
  predict(newdata = tibble(year = 2020)) %>% 
  round()
```

Predict TB cases in 2020 for each country

```{r}
tb_predictions <-
  tb %>% 
  group_by(country, year) %>% 
  summarise(n = sum(n)) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(n ~ year, data = .))) %>%
  mutate(pred = map_dbl(model, predict, tibble(year = 2020))) %>%
  mutate(pred = round(pred))
```

Things that are easy to do:

* Which countries will have the most cases?
* What does the data look like for India?
* How do the Korea's compare?
* How good were the models?

```{r}

```


***

Take Aways

* Use `View()` to inspect lists
* Use `pluck()`, `[[ ]]`, or `$` to extract values from lists
* Use purrr's `map()` functions to manipulate lists
* Lists can be a column in a data frame
* Tables are an organizational structure that you can manipulate.
