---
title: "Models"
---

```{r setup, message=FALSE}
library(tidyverse)
library(modelr)
library(broom)

wages <- heights %>% filter(income > 0)
```

## Your Turn 1

Fit the model on the slide and then examine the output. What does it look like?

```{r}

```

## Your Turn 2

Use a pipe to model `log(income)` against `height`. Then use broom and dplyr functions to extract:

1. The **coefficient estimates** and their related statistics 
2. The **adj.r.squared** and **p.value** for the overall model

```{r}

```


## Your Turn 3

Model `log(income)` against `education` and `height` and `sex`. Can you interpret the coefficients?

```{r}

```

## Your Turn 4

Add `+ geom_smooth(model = lm)` to the code below. What happens?

```{r}
wages %>%
     ggplot(aes(x = height, y = log(income))) +
     geom_point(alpha = 0.1)
```

## Help Me

```{r}

```


## Your Turn 5

Use `gather_residuals` to complete the code below, which compares the residuals of all three models, `mod_h`, `mod_eh`, and `mod_ehs`.

```{r warning = FALSE, message = FALSE}

# In case you haven't made the three models
mod_h <- wages %>% lm(log(income) ~ height, data = .)
mod_eh <- wages %>% lm(log(income) ~ education + height, data = .)
mod_ehs <- wages %>% lm(log(income) ~ education + height + sex, data = .)

# Be sure to remove or comment out each _ before running the code
wages %>% 
  _____________(______, ______, ______) %>% 
  ggplot() ___ 
    geom_histogram(aes(x = ______)) +
    facet_grid(_____ ~ .)
```

***

# Take Aways

* Use `glance()`, `tidy()`, and `augment()` from the **broom** package to return model values in a data frame.

* Use `add_predictions()` or `gather_predictions()` or `spread_predictions()` from the **modelr** package to visualize predictions.

* Use `add_residuals()` or `gather_residuals()` or `spread_residuals()` from the **modelr** package to visualize residuals.
